Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-29 paper.tex
did some edits

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold. In our paper, we assume all arms are some agents' best arm. Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm. \bccomment{We need a stronger condition, see corralary 1} If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$. The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.  Essentially, heterogeneity provides free exploration.  These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.

@@

Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
\begin{align}
&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,\tau)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
\end{align}

@@

Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}<-N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}

@@

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Nn$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

\begin{proof}
	A round completes when each arm is pulled at least once in that round. Let $X_{i}$ be the number of agents who come to the system between the time after the $i-1^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled. Then we know 
\begin{equation*}
\mathbb{E}[t_{n}-t_{n-1}]=\sum_{i=1}^{N}E[X_{i}].
\end{equation*}

@@

Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.  Thus,
\begin{align}
E[t_{n}-t_{n-1}]\leq Nn. \nonumber
\end{align}
\end{proof}

@@

We know
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

@@

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
\end{align}

@@

\begin{align}
&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
\end{align}

@@

\begin{lemma}
Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
\label{lemma:numP}
\end{lemma}

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:

@@

Thus, we know
\begin{align}
&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
\end{align}

@@

Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
&\bccomment{\text{is the following proof correct?}} \nonumber \\
= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
\end{align}

@@

For a fixed $T$, we only need to minimizing the following two terms since all others are constant:

>>>>

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold. In our paper, we assume all arms are some agents' best arm. Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm. If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$. The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.  Essentially, heterogeneity provides free exploration.  These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.

@@

Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
\begin{align}
&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
\end{align}

@@

Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}
Similarily, we can bound 
\begin{align}
&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
\end{align}

Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$. Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
\end{align}

@@

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

\begin{proof}
	A round completes when each arm is pulled at least once in that round. Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled. Then we know 
\begin{equation*}
\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
\end{equation*}

@@

Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.  Thus,
\begin{align}
E[t_{n+1}-t_{n}]\leq Nn. \nonumber
\end{align}
\end{proof}

@@

Based on the above notations, we can rewrite the cumulative payment as follows:
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
\end{align}

@@

We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
\begin{align}
&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
\leq &\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
\end{align}

@@

\begin{align}
&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
\end{align}

@@

\begin{lemma}
The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
\label{lemma:numP}
\end{lemma}

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).

@@

The cumulative expected number of payments is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
\end{align}

@@

Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
\end{align}

@@

For a fixed $T$, we only need to minimize the following two terms since all others are constant:
